Overview of the eHealth Knowledge Discovery Challenge at IberLEF 2021

### 2021-06-19 paper/paper.tex
Add figure

\documentclass[a4paper,11pt,twocolumn,twoside]{article}
\usepackage[dvips]{graphicx}
\usepackage{sepln_en}
\usepackage{fullname}
\usepackage[utf8]{inputenc}
\usepackage{booktabs}
\usepackage{tabularx}
% \usepackage[spanish,es-nosectiondot, es-tabla, es-noindentfirst, es-nolists]{babel}

@@

A custom annotation model has been defined, comprising 4 entity types and 13 relations,
that attempts to capture a large part of factual semantics in technical documents,
including enciclopedias, news, and scientific papers.

The annotation model is explained in detail in \namecite{piad2019general}.

A brief explanation is presented next.

-- Explicar las entidades y relaciones como siempre.

The challenge has been divided into two different subtasks:
entity recognition and relation extraction.

\subsection{Subtask A: Entity recognition}
Given a list of eHealth documents written in Spanish, the goal of this subtask is to identify all the entities per document and their types. These entities are all the relevant terms (single word or multiple words) that represent semantically important elements in a sentence. The following figure shows the relevant entities that appear in a set of example sentences.

@@

Concept: indentifies a relevant term, concept, idea, in the knowledge domain of the sentence.
Action: indentifies a process or modification of other entities. It can be indicated by a verb or verbal construction, such as “afecta” (affects), but also by nouns, such as “exposición” (exposition), where it denotes the act of being exposed to the Sun, and “daños” (damages), where it denotes the act of damaging the skin. It can also be used to indicate non-verbal functional relations, such as “padre” (parent), etc.
Predicate: identifies a function or filter of another set of elements, which has a semantic label in the text, such as “mayores” (older), and is applied to an entity, such as “personas” (people) with some additional arguments such as “60 años” (60 years).
Reference: identifies a textual element that refers to an entity –of the same sentence or of different one–, which can be indicated by textual clues such as “esta”, “aquel”, etc.

@@

General relations (6): general-purpose relations between two concepts (it involves Concept, Action, Predicate, and Reference) that have a specific semantic. When any of these relations applies, it is preferred over a domain relation –tagging a key phrase as a link between two information units–, since their semantic is independent of any textual label:

is-a: indicates that one entity is a subtype, instance, or member of the class identified by the other.
same-as: indicates that two entities are semantically the same.
has-property: indicates that one entity has a given property or characteristic.
part-of: indicates that an entity is a constituent part of another.
causes: indicates that one entity provoques the existence or occurrence of another.
entails: indicates that the existence of one entity implies the existence or occurrence of another.
Contextual relations (3): allow to refine an entity (it involves Concept, Action, Predicate, and Reference) by attaching modifiers. These are:

in-time: to indicate that something exists, occurs or is confined to a time-frame, such as in “exposición” in-time “verano”.
in-place: to indicate that something exists, occurs or is confined to a place or location.
in-context: to indicate a general context in which something happens, like a mode, manner, or state, such as “exposición” in-context “prolongada”.
Action roles (2): indicate which role play the entities related to an Action:

subject: indicates who performs the action, such as in “[el] asma afecta […]”.
target: indicates who receives the effect of the action, such as in “[…] afecta [las] vías respiratorias”. Actions can have several subjects and targets, in which case the semantic interpreted is that the union of the subjects performs the action over each of the targets.
Predicate roles (2): indicate which role play the entities related to a Predicate:

domain: indicates the main entity on which the predicate applies.
arg: indicates an additional entity that specifies a value for the predicate to make sense. The exact semantic of this argument depends on the semantic of the predicate label, such as in “mayores [de] 60 años”, where the predicate label “mayores” indicates that “60 años” is a quantity, that restricts the minimum age for the predicate to be true.

@@

-- Fórmulas
Rec_{AB} = \frac{C_A + C_B + \frac{1}{2} P_A}{C_A + I_A + C_B + P_A + M_A + M_B}

Prec_{AB} = \frac{C_A + C_B + \frac{1}{2} P_A}{C_A + I_A + C_B + P_A + S_A + S_B}

F_{1AB} = 2 \cdot \frac{Prec_{AB} \cdot Rec_{AB}}{Prec_{AB} + Rec_{AB}}

>>>>

\documentclass[a4paper,11pt,twocolumn,twoside]{article}
\usepackage{graphicx}
\usepackage{sepln_en}
\usepackage{fullname}
\usepackage[utf8]{inputenc}
\usepackage{booktabs}
\usepackage{tabularx}
% \usepackage[spanish,es-nosectiondot, es-tabla, es-noindentfirst, es-nolists]{babel}

@@

A custom annotation model has been defined, comprising 4 entity types and 13 relations,
that attempts to capture a large part of factual semantics in technical documents,
including enciclopedias, news, and scientific papers. The annotation model is explained in detail in \namecite{piad2019general}. Figure~\ref{fig:model} shows an illustrative example of the annotation model in three Spanish sentences.
The challenge has been divided into two different subtasks: entity recognition and relation extraction.

\begin{figure*}
  \includegraphics[width=\textwidth]{model.png}
  \caption{Examples the annotation model defined for the eHealth-KD Challenge.\label{fig:model}}
\end{figure*}

\subsection{Subtask A: Entity recognition}

Given a list of eHealth documents written in Spanish, the goal of this subtask is to identify all the entities per document and their types. These entities are all the relevant terms (single word or multiple words) that represent semantically important elements in a sentence. The following figure shows the relevant entities that appear in a set of example sentences.

@@

\begin{description}
  \item[Concept:] indentifies a relevant term, concept, idea, in the knowledge domain of the sentence.
  \item[Action:] indentifies a process or modification of other entities. It can be indicated by a verb or verbal construction, such as “afecta” (affects), but also by nouns, such as “exposición” (exposition), where it denotes the act of being exposed to the Sun, and “daños” (damages), where it denotes the act of damaging the skin. It can also be used to indicate non-verbal functional relations, such as “padre” (parent), etc.
  \item[Predicate:] identifies a function or filter of another set of elements, which has a semantic label in the text, such as “mayores” (older), and is applied to an entity, such as “personas” (people) with some additional arguments such as “60 años” (60 years).
  \item[Reference:] identifies a textual element that refers to an entity –of the same sentence or of different one–, which can be indicated by textual clues such as “esta”, “aquel”, etc.
\end{description}

@@

\paragraph{General relations (6)}: general-purpose relations between two concepts (it involves Concept, Action, Predicate, and Reference) that have a specific semantic. When any of these relations applies, it is preferred over a domain relation –tagging a key phrase as a link between two information units–, since their semantic is independent of any textual label:

\begin{description}
  \item[is-a:] indicates that one entity is a subtype, instance, or member of the class identified by the other.
  \item[same-as:] indicates that two entities are semantically the same.
  \item[has-property:] indicates that one entity has a given property or characteristic.
  \item[part-of:] indicates that an entity is a constituent part of another.
  \item[causes:] indicates that one entity provoques the existence or occurrence of another.
  \item[entails:] indicates that the existence of one entity implies the existence or occurrence of another.
\end{description}

\paragraph{Contextual relations (3)}: allow to refine an entity (it involves Concept, Action, Predicate, and Reference) by attaching modifiers. These are:

\begin{description}
  \item[in-time:] to indicate that something exists, occurs or is confined to a time-frame, such as in “exposición” in-time “verano”.
  \item[in-place:] to indicate that something exists, occurs or is confined to a place or location.
  \item[in-context:] to indicate a general context in which something happens, like a mode, manner, or state, such as “exposición” in-context “prolongada”.
\end{description}

\paragraph{Action roles (2):} indicate which role play the entities related to an Action:

\begin{description}
  \item[subject:] indicates who performs the action, such as in “[el] asma afecta […]”.
  \item[target:] indicates who receives the effect of the action, such as in “[…] afecta [las] vías respiratorias”. Actions can have several subjects and targets, in which case the semantic interpreted is that the union of the subjects performs the action over each of the targets.
\end{description}

\paragraph{Predicate roles (2):} indicate which role play the entities related to a Predicate:

\begin{description}
  \item[domain:] indicates the main entity on which the predicate applies.
  \item[arg:] indicates an additional entity that specifies a value for the predicate to make sense. The exact semantic of this argument depends on the semantic of the predicate label, such as in “mayores [de] 60 años”, where the predicate label “mayores” indicates that “60 años” is a quantity, that restricts the minimum age for the predicate to be true.
\end{description}

@@

-- Fórmulas
$$Rec_{AB} = \frac{C_A + C_B + \frac{1}{2} P_A}{C_A + I_A + C_B + P_A + M_A + M_B}$$

$$Prec_{AB} = \frac{C_A + C_B + \frac{1}{2} P_A}{C_A + I_A + C_B + P_A + S_A + S_B}$$

$$F_{1AB} = 2 \cdot \frac{Prec_{AB} \cdot Rec_{AB}}{Prec_{AB} + Rec_{AB}}$$
